### 2019-12-13 README.Rmd
added published paper to README

[![badge](https://img.shields.io/badge/Launch-Analysis-lightblue.svg)](https://mybinder.org/v2/gh/seabbs/DirectEffBCGPolicyChange/master?urlpath=rstudio)
[![Documentation](https://img.shields.io/badge/Documentation-click here!-lightgrey.svg?style=flat)](https://www.samabbott.co.uk/DirectEffBCGPolicyChange)
[![Paper](https://img.shields.io/badge/Paper-10.1101/567511-lightgreen.svg)](https://doi.org/10.1101/567511)
[![DOI](https://zenodo.org/badge/173767331.svg)](https://zenodo.org/badge/latestdoi/173767331)

>>>>

[![badge](https://img.shields.io/badge/Launch-Analysis-lightblue.svg)](https://mybinder.org/v2/gh/seabbs/DirectEffBCGPolicyChange/master?urlpath=rstudio)
[![Documentation](https://img.shields.io/badge/Documentation-click here!-lightgrey.svg?style=flat)](https://www.samabbott.co.uk/DirectEffBCGPolicyChange)
[![Paper](https://img.shields.io/badge/Paper-10.2807%2F1560--7917.ES.2019.24.49.1900220-lightgreen)](https://doi.org/10.1016/j.vaccine.2019.06.056)
[![Preprint](https://img.shields.io/badge/Preprint-10.1101/567511-lightgrey.svg)](https://doi.org/10.1101/567511)
[![DOI](https://zenodo.org/badge/173767331.svg)](https://zenodo.org/badge/latestdoi/173767331)
